Congestion-Aware Join Optimization in Key-Value Stores

### 2014-08-08 paper/paper.tex
Switch away from ACM alternate style
Use full size biliography
Adds last figure & last bit text of the paper

\documentclass{sig-alternate-2013}

@@

\subsection{Micro Benchmark}
\begin{figure}
    \centering
    \includegraphics[scale=2.5]{figures/Join_micro_benchmark.png}
    \caption{Micro benchmark setup}\label{fig:micro_benchmark}
\end{figure}

@@

@@

There are many opportunities to combine this work with appropriate key placement strategies for further performance optimizations.
A key placement strategy which is network and workload aware may provide significant performance advantages.
On the flip side of the data placement problem is the problem of data shipping, where we can exploit our system's network awareness to decide where data should be shipped to execute joins most efficiently.
Futhermore, our current query execution model is very simplistic and could be expanded to support richer queries and distributed index data structures.
We would also like to investigate other query types such as aggregation which we suspect would also benefit from our approach.
This presents new challenges in network scheduling, especially in the face of concurrent queries of multiple different types.

@@

\let\theOLDbibliography\thebibliography\renewcommand{\thebibliography}[1]{\theOLDbibliography{#1}%
\item[]\vspace*{0.5mm}}

\bibliographystyle{abbrv}
{\scriptsize
\bibliography{paper}
}

>>>>

\documentclass{acm_proc_article-sp}

@@

\subsection{Micro Benchmark}
\begin{figure}
    \centering
    \includegraphics[scale=2]{figures/Join_micro_benchmark.png}
    \caption{Micro benchmark setup}\label{fig:micro_benchmark}
\end{figure}

@@

To understand how link capacity affects the perform. We also tested our micro benchmark by varying the link capacity. The result is shown in figure~\ref{fig:varying_bd}. During each of the experiment, the system parameters, e.g. the minimum bandwidth guarantee for each server (server 1 will always have min-guarantee off 80\% of the total link capacity), are fixed and we only varied the link capacity. We see that our system can adaptively work with different link capacities and our system is uniformly performing better than the baseline system without scheduling. The next promising step is to increase link capacity at larger steps and study how system will react and try to learn if we need to adjust system adaptivity to the link capacity.

\begin{figure}
    \centering
    \includegraphics[scale=0.47]{figures/simple_topo_varying_bd.png}
    \caption{Query completion time with varying link capacity}\label{fig:varying_bd}
\end{figure}

@@

There are many opportunities to combine this work with appropriate key placement strategies for further performance optimizations.
A key placement strategy which is network and workload aware may provide significant performance advantages.
On the flip side of the data placement problem is the problem of data shipping, where we can exploit our system's network awareness to decide where data should be shipped to execute joins most efficiently.
Furthermore, our current query execution model is very simplistic and could be expanded to support richer queries and distributed index data structures.
We would also like to investigate other query types such as aggregation which we suspect would also benefit from our approach.
This presents new challenges in network scheduling, especially in the face of concurrent queries of multiple different types.

@@

\bibliographystyle{abbrv}
\bibliography{paper}
